{\LARGE Model Selection for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-01-31 Paper/main.tex
fpcr estimation theory

	\begin{equation}\label{KarhunenLoeve}
		X(\omega)(t) = \mu(t) + \sum_{j = 1}^{\infty} \xi_j(\omega) \nu_j(t)
	\end{equation}

@@

	\begin{equation}
		\tilde{\xi}^{m,L}_{i} = \sum_{j = 1}^{L} \left[ a_{i,j}\sum_{k = 1}^{L} b_{k}^m \int_{0}^{1} \phi_j(s) \phi_{k}(s)\mathrm{d}s\right]
	\end{equation}

@@

	This representation translates the original problem of regressing a scalar on a continuously observed function to a problem where a scalar is regressed on a countably infinite sequence of regressors. Using a truncation of the basis at some parameter $L$ can be used to make this problem tractable with typical theory from multivariate regression while staying reasonably accurate.

@@

	% maybe use n for coefficents in expansion of nu? before b for beta, so this could be a consistent choice

>>>>

	\begin{equation}\label{KarhunenLoeve}
		X(\omega)(t) = \mu(t) + \sum_{m \in \mathcal{M}} \xi^m(\omega) \nu^m(t)
	\end{equation}

@@

	\begin{equation}
		\hat{\xi}_{i}^m \approx \sum_{j = 1}^{L} \left[ a_{i,j}\sum_{k = 1}^{L} b_{k}^m \int_{0}^{1} \phi_j(s) \phi_{k}(s)\mathrm{d}s\right] =: \tilde{\xi}^{m,L}_{i}
	\end{equation}

@@

	This representation translates the original problem of regressing a scalar on a continuously observed function to a problem where a scalar is regressed on what is possibly a countably infinite sequence of regressors. Using a truncation of the basis at some parameter $L$ can be used to make this problem tractable with typical theory from multivariate regression while staying reasonably accurate.

@@

	{\color{red} We have to clean this up theoretically. Having both the mean function and the $\alpha$ in there makes this viable for the model but not for estimation as are estimated in the constant.}

	\begin{equation}
		\begin{split}
			Y(\omega) &= \alpha + \int_{0}^{1} {\color{red}X(\omega)(s)} {\color{blue}\beta(s)} \mathrm{d}s + \epsilon(\omega)
			= \alpha + \int_{0}^{1} {\color{red}\left(\mu(s) + \sum_{m \in \mathcal{M}} \xi^m(\omega) \nu^m(s)\right)} {\color{blue}\left(\sum_{j \in \mathcal{I}} b_j \phi_j(s)\right)} \mathrm{d}s + \epsilon(\omega)\\
			&= \alpha + \int_{0}^{1} \left[ \sum_{j \in \mathcal{I}} b_j \phi_j(s) \mu(s) + \sum_{j \in \mathcal{I}} \left[b_j \sum_{m \in \mathcal{M}} \xi^m(\omega) \nu^m(s) \phi_j(s)\right] \right] \mathrm{d}s + \epsilon(\omega) \\
			&= \alpha + \sum_{j \in \mathcal{I}} b_j \int_{0}^{1} \phi_j(s) \mu(s) \mathrm{d}s + \sum_{j \in \mathcal{I}} \left[b_j \sum_{m \in \mathcal{M}} \xi^m(\omega) \int_{0}^{1}\nu^m(s) \phi_j(s) \mathrm{d}s \right] + \epsilon(\omega) \\
			& \approx \alpha + \sum_{j = 1}^{J} b_j \int_{0}^{1} \phi_j(s) \mu(s) \mathrm{d}s + \sum_{j = 1}^{J} \left[b_j \sum_{m  = 1}^{M} \xi^m(\omega) \int_{0}^{1}\nu^m(s) \phi_j(s) \mathrm{d}s \right] + \epsilon(\omega)
		\end{split}
	\end{equation}

	Using sample analogues, we can use this form to obtain the following approximation.

	\begin{equation}
			Y(\omega) \approx \alpha + \sum_{j = 1}^{J} b_j \int_{0}^{1} \phi_j(s) \hat{\mu}(s) \mathrm{d}s + \sum_{j = 1}^{J} \left[b_j \sum_{m  = 1}^{M} \hat{\xi}^m(\omega) \int_{0}^{1} \hat{\nu}^m(s) \phi_j(s) \mathrm{d}s \right] + \epsilon(\omega)
	\end{equation}

	Using the same basis for the construction of $\tilde{\xi}^{m,L}_{i}$ and the expansion of the coefficient function and the same truncation parameter $L$ for both approximations, then gives us the following.

	\begin{equation}
		y_i \approx \alpha + \sum_{j = 1}^{L} b_j \int_{0}^{1} \phi_j(s) \hat{\mu}(s) \mathrm{d}s + \sum_{j = 1}^{L} \left[b_j \sum_{m  = 1}^{M}  \tilde{\xi}^{m,L}_{i} \int_{0}^{1} \hat{\nu}^m(s) \phi_j(s) \mathrm{d}s \right] + \epsilon(\omega)
	\end{equation}
